SSA based global code motion of identical computations

### 2017-04-14 hoist.tex
thank

% TODO: References
% Sink instructions
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna

@@

\section{Acknowledgments}
We would like to thank Daniel Berlin for his code reviews and for his feedback
on earlier versions of this paper.

>>>>

% TODO: References
% Sink instructions
% Ranking of instructions from Zadeck
% Liveness analysis from Ramakrishna
% Experimental results: Register spills, compile time, run time.

@@

\section{Acknowledgments}
We would like to thank Daniel Berlin for his code reviews and for his feedback
on earlier versions of this paper and Brian Grayson for motivating examples that
started this work.
